Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-21 surfaces-write-up/surface-write-up.tex
two pts p^1 remark edit last sentence precisely
remove some completed todos
added linebreaks

\maketitle
\todo{make title shorter so it doesn't overlap with page numbers}
\todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most''}

@@

\noindent
Figure ~\ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
\end{rem}
\todo{possibly define mediant}

@@

\begin{rem}
\label{rem:proj-two-points}
Note that we cannot extend this result to the case when
$D$ is supported at two hypersurfaces with arbitrary rational
coefficients in the same manner that O'Dorney does for the
$\bp^1$ case \cite[Section 4]{dorney:canonical}. As will be shown
in Example ~\ref{eg:hyperplane}, the degrees of generation of the
canonical ring of a general $\bq$-divisor supported on two
hyperplanes cannot be bounded so tightly. The two-point
$\bp^1$ result leverages particular facts about the structure of
$\bp^1$. \todo{Possibly say what facts?}
\end{rem}

@@

Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n {y_j}^{c_j}$.  Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in \Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$ component $-\alpha_j d_j + \kappa_j$ and let $e_{i,j}$ (when it exists) lie in degrees $d_{i,j}$ with $i^{th}$ component $\kappa_{i,j}'$ and $j^{th}$ component $\kappa_{j,i}''$.
Then a careful computation deduces that 
%if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
\[
	\sigma = \lambda + E
\]
where $\lambda \in \Sigma$ and
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \br, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \br, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}

>>>>

\maketitle
\todo{Aaron: Standardize generation in degree ... phrasing. I like ``generation in degree at most''}

@@

\noindent
Figure ~\ref{fig:s14/5-lattice} gives a pictorial representation of the positive best lower approximations of $\alpha = \frac{14}{5}$.
\end{rem}

@@

\begin{rem}
\label{rem:proj-two-points}
Note that we cannot extend this result to the case when
$D$ is supported at two hypersurfaces with arbitrary rational
coefficients in the same manner that O'Dorney does for the
$\bp^1$ case \cite[Section 4]{dorney:canonical}. As will be shown
in Example ~\ref{eg:hyperplane}, the degrees of generation of the
canonical ring of a general $\bq$-divisor supported on two
hyperplanes cannot be bounded so tightly. The two-point
$\bp^1$ result leverages the fact that $\bp^1$ has two
independent coordinates.
\end{rem}

@@

Let $\sigma\in \Sigma'$ correspond to the monomial $y_i \prod_{j=1}^n
{y_j}^{c_j}$.  Then we can write $\sigma$ as a sum of $r_j e_j$'s for $j\in
\Te$ and $r_{j,k}e_{j,k}$ for $j\in \Tp, k\in \Tm$.  
For convenience, let $e_j$ (when it exists) be in degree $d_j$ with $j^{th}$
component $-\alpha_j d_j + \kappa_j$ and let $e_{i,j}$ (when it exists) lie in
degrees $d_{i,j}$ with $i^{th}$ component $\kappa_{i,j}'$ and $j^{th}$
component $\kappa_{j,i}''$.
Then a careful computation implies that 
%if $i\in \Te$, $i\in \Tp$, and $i\in \Tm$, then
\[
	\sigma = \lambda + E
\]
where $\lambda \in \Sigma$ and
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \br, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \br, \sum_{j\in \Tm} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}
